\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 arch.tex
heading changes based on Minh and discussion; also noted FP comments
Extra typos an rewording

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update. By doing so, the planner is
  better informed in its deliberation despite a larger latency than
  the changing world.

Systematic partitioned inference is a major contribution of
\rx. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a significant implication on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to our framework by first
linking concepts in temporal planning with the \rx framework. Note
that in the following treatise, we call the formal semantic framework
of \rx as the 'agent'. Reactors constitute an entity within this agent
and are standalone blocks of inference. The scope, detail and number
of reactors are application specific and outside the scope of this
chapter.

@@

\subsection{The  \eu Deliberative Reactor}
\label{sec:arch:europa}

Within \rx, an instance of an \eu reactor comes with the sole purpose
to deliberate. A typical design of such a reactor takes its cues from
\texttt{IDEA} \cite{mus02, mus06} where both planning and execution
are based on a single unified model within a rich representation that
provides support for temporal inference. In \rx, the execution cycle
consists of two deliberation processes which are implemented as two
separate \eu solvers modifying the \emph{same} plan database.

@@

Consider for example the Shopping Agent model where the timeline 
\texttt{Agent.position} is {\em external} while \texttt{Agent} is
implemented a an {\em internal} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.

\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}

>>>>

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update in the {\em same} polan
  database used for planning. By doing so, the planner is
  better informed in its deliberation despite a larger latency than
  the changing world. 
\end{itemize}

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a significant implication on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to our framework by first
linking concepts in temporal planning with the \rx framework. Note
that in the following treatise, we call the formal semantic framework
of \rx as the 'agent'. Reactors constitute an entity within this agent
and are standalone blocks of inference. The scope, detail and number
of reactors are application specific and outside the scope of this
chapter.

@@

It is important to note that, in T-REX architecture, the only critical
task of a reactor is to successfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trusted anymore and results on this reactor exclusion from the
execution cycle and consequent destruction. As the agent destroy 
the  faulty reactor is destroyed the agent produced on all of 
its former {\em internal} timelines the special observation 
\texttt{Failed} to all the reactors which did declare these state 
variables as {\em external} informing
them through this that this specific state variable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the failure to find a plan for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can identify that, from
  now on, there's no way to take water samples. It still can 
  navigate as \texttt{Pilot} is available which allow him to continue
  this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

\subsection{The  Deliberative Reactor}
\label{sec:arch:europa}

Within \rxe, an instance of an \eu reactor comes with the sole purpose
to deliberate. A typical design of such a reactor takes its cues from
\texttt{IDEA} \cite{mus02, mus06} where both planning and execution
are based on a single unified model within a rich representation that
provides support for temporal inference. In \rxe, the execution cycle
consists of two deliberation processes which are implemented as two
separate \eu solvers modifying the \emph{same} plan database.

@@

Consider for example the Shopping Agent model where the timeline 
\texttt{Agent.position} is {\em external} while \texttt{Agent} is
implemented a an {\em internal} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.
x1
\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}
